### 2020-09-08 paper/sections/introduction.tex
minor ab and intro

Apparently, choosing different configurations will affect resource consumption and accuracy. For example, using a complex model and high resolution can obviously accurately detect the target object, but it also requires more computing resources. However, choosing a simple model and low resolution can significantly reduce resource consumption, although it reduces the accuracy to some extent. And in the case of a highway video analytics, due to the rate of car travel cannot be predicted in advance, so when the car drives slowly (or static) because of the traffic jam, we can choose a lower frame rate (such as 1 FPS) without having to use a fixed on the whole video higher frame rate, this can significantly reduce resource consumption, but does not affect the accuracy of the video analytics.

@@

\begin{itemize}	
\item \emph{The best configuration for a video analytics pipeline changes over time with the environment.} The real-word environment is non-stationary; for instance, tracking vehicles when traffic moves quickly requires a much higher frame rate than when traffic moves slowly, but when each condition occurs may vary by hour, minute, or second. As a dynamic video analytics configuration solution, we target to provide a solution that dynamically picks a configuration according to intrusive dynamics of video contents, i.e., it can \emph{generate} video analytics configuration for video analytics in a different time.

>>>>

Apparently, choosing different configurations will affect resource consumption and accuracy. For example, using a complex model with high resolution can obviously and accurately detect the target object, but it also requires more computing resources. However, choosing a simple model with low resolution can significantly reduce resource consumption, although it reduces the accuracy to some extent. Obviously, when the target car (object) is large, a smaller model and a lower resolution can meet the accuracy with a large reduction of resource consumption, while the target car (object) is small, a more complex model and higher resolution are needed to achieve a satisfactory accuracy. And in the case of a highway video analytics, due to the rate of car travel cannot be predicted in advance, so when the car drives slowly (or static) because of the traffic jam, we can choose a lower frame rate (such as 1 FPS) instead of having to use a constant high frame rate throughout whole video. This can significantly reduce resource consumption, but does not affect the accuracy of the video analytics.

@@

\begin{itemize}	
\item \emph{The best configuration for a video analytics pipeline changes over time with the environment.} The real-world environment is non-stationary; for instance, tracking vehicles when traffic moves quickly requires a much higher frame rate than when traffic moves slowly, but when each condition occurs may vary by hour, minute, or second. As a dynamic video analytics configuration solution, we target to provide a solution that dynamically picks a configuration according to intrusive dynamics of video contents, i.e., it can \emph{generate} video analytics configuration for video analytics in a different time.
